---
title: "Does the hype work?"
subtitle: "Social Media's influence on Book Sales"
author: "Maya Gutierrez"
title-slide-attributes:
  data-slide-number: none
format: revealjs
editor: visual
execute:
  echo: false
---

```{r}
#| label: load-packages
#| include: true

library(tidyverse)
library(readr)
library(dplyr)
library(tidyr)

```

```{r}
#| label: page2
#| include: false

# For better figure resolution
knitr::opts_chunk$set(
  fig.retina = 3, 
  dpi = 300, 
  fig.width = 6, 
  fig.asp = 0.618, 
  out.width = "70%"
  )
```

```{r}
#| label: load_data
#| include: true

amazontop_Sheet1 <- read_csv("data/amazontop - Sheet1.csv")

Bookish_Data_Responses_Actual_sm <- read_csv("data/Bookish Data (Responses) Actual - sm.csv")
  
bookishdata_genre1 <- read_csv("data/bookishdata - genre1.csv")
#View(bookishdata_genre1)

bookishdata_books <- read_csv("data/bookishdata - books.csv")
# View(bookishdata_books)



```

My project was the data collection and analysis of social media's impact on book sales.

I found a pre-scrapped csv file online of Amazon's top 100 bestselling books and decided to partner this with my own collected data from "Bookish" social media sites and communities.

Essentially, I asked about genre's, social media usage, and book recognition to those who considered themselves active on bookish social media.

## Data Collection

\- My target was Reed Students

-   I received 33 responses

-   The Questionnaire was roughly 200 questions

-   I ended my Questionnaire officially on Monday the 15th.

# Questionnaire Demographics

```{r, echo=FALSE}
#| label: sm_load
#| include: true
social_media_averages <- Bookish_Data_Responses_Actual_sm %>%
  pivot_longer(cols = c("sm_tok", "sm_tube", "sm_gram", "sm_good", "sm_red", "sm_red", "sm_tumb", "sm_oth"), names_to = "variable", values_to = "value") %>%
  group_by(variable) %>%
  summarise(
    average = mean(value, na.rm = TRUE))

social_media_averages <- social_media_averages %>%
  mutate(social_media = variable) %>%
  select(-variable)
```

```{r}
ggplot(social_media_averages, aes(x = social_media, y = average)) + 
  geom_bar(stat = "identity") + labs(x= "Social Media Types", y= "Average on a Scale of 0-1", title = "What Bookish Social Media Are you a part of?")
```

## Genre Breakdown

```{r, echo= FALSE}
genre_tidy <- separate_rows(amazontop_Sheet1, genre, sep = ",\\s*")

genre_counts <- as.data.frame(table(genre_tidy$genre))
colnames(genre_counts) <- c("genre", "count")
genre_counts<- genre_counts %>% mutate(proportion= count/ sum(count))

genre_counts <- genre_counts %>% arrange(desc(proportion))
slice_head(genre_counts, n= 10)
```

\#

## Leading Genres

```{r, echo= FALSE}
originalgenredistribution <- genre_counts %>%
  filter(count > 2) %>%
  arrange(desc(genre))

originalhisto <- ggplot(originalgenredistribution, aes(x = genre, y = count, fill = count > 10)) +
  geom_bar(stat = "identity", show.legend = FALSE) +  
  scale_fill_manual(values = c("FALSE" = "#3182bd", "TRUE" = "#de2d26")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1),
        panel.background = element_rect(fill = "white"))

originalhisto
```

```{r, echo= FALSE}

numeric_cols <- sapply(bookishdata_genre1, is.numeric)

# Pivot the data frame
genre_averages <- bookishdata_genre1 %>%
  pivot_longer(cols = names(bookishdata_genre1)[numeric_cols], names_to = "genre", values_to = "value") %>%
  group_by(genre) %>%
  summarise(
    averagescore = mean(value, na.rm = TRUE),
    low = quantile(value, 0.1, na.rm = TRUE),
    high = quantile(value, 0.9, na.rm = TRUE)
  )

merged_genre<- merge(genre_averages, genre_counts, by = "genre")

# View the merged dataset
print(merged_genre)
```

```{r, echo= FALSE}
ggplot(merged_genre, aes(x=proportion, y=averagescore)) + geom_point() + labs(x= "Proportion of Amazon's Top 100", y= "Average Social Media presence Scale 0-2", title= "Bestselling Makeup by Genre and Social Media Presence Rating")
```

```{r, echo = FALSE} 
genremodel <- lm(proportion ~ averagescore, data = merged_genre)

summary(genremodel)
```
