---
title: "Project 2"
subtitle: "Proposal"
authors: ""
format: html
editor: visual
---

```{r load-packages}
#| label: load-pkgs
#| message: false
#| warning: false

library(tidyverse)
```

## Dataset

```{r load-data}
#| label: load-data
#| message: false

## read data 
```

## Reason for Choosing this Dataset

## Questions and Analysis Plan

-   Using a combination of scraped data from amazon's top 100 bestsellers and data collected myself, I will graphically demonstrate how presence on social media impacts a books rating and ranking.

-   The first data set is a pre-scraped data-set I found on "Kaggle". It took the top 100 bestselling books for Amazon at the time (November 2023) and placed them on a data frame. Some important variables include book name, author, price, rating and genre. There are 100 observations with each observation being a from the bestsellers list. The data comma-separated value file already comes in ranked order.

    ```{r}
    library(readr)
    Top_100_Trending_Books <- read_csv("GitHub/project-02-bookish_trends/`Top-100 Trending Books.csv`")
    View(Top_100_Trending_Books)
    ```

    -   The second component of data is one I collect myself. I am going to put out a Google form where those who frequently involved in book social media communities can answer some questions. The data from the Google form will all be accessed via Google spreadsheet. This spreadsheet can be easily turned into a csv file that I will open in r-studio.

        -   In order to maintain a tidy format I will be using the multiple choice grid option of the Google forms. This will also make things easier for those filling out the Google form.

        -   For genre I will have one question dedicated to asking about genres are the most prevalent on online readings spheres. I will ask about each genre specifically and how prominent the genre is on social media on a 0-2 scale. I will assign the numerical values in r-studio. Those filling out the form will not see the numerical values.

            -   0 means no social media presence.

            -   1 means some social media presence.

            -   2 means a high social media presence.

        -    I wanted to next hone in on specific authors and books and ask if each book individually has a social media presence. Like with genre above I will go by book individually.

        -   One question will be dedicated to determining what online reading spaces specifically a person frequents. Not only will this reveal the demographics of those filling out the form. I will be able to decipher if some books are more hyped on some platforms than others.

-   The reason why I am going so far as to collect my own data is because attempting to find data about online book trends is difficult with so many having different user experiences. I attempted to access the Tik-Tok API, but unfortunately I do not meet the credentials necessary to have access to free content data. Other social media platforms had similar challenges. I have always had an assumption that social media has impacted what products are popular. I myself frequent these platforms and would be interested in what the data actually does say.

-   The final organization of your project repository. This means describing the project organization in your proposal as well as implementing that organization in your repo. Create any folders needed and place a `README.md` in each folder explaining what goes in there.
